\documentclass[10pt]{CurriculumVitae}
  
\name{Antonio Sánchez Gómez}
\githubaccount{antsago}
\linkedin{antsago}

\begin{document}

  \makeheading

  \section{Personal profile}
    {
      I am a Senior Fullstack Javascript Developer with a mushroom-shaped profile.
      My core expertise lies in distributed systems –microservices and microfrontends– from where it radiates into adjacent fields. I am a junior-to-mid UI designer and developer, fluent in Docker, familiar with people management and AI, and able to understand the language of QA and DevOps engineers.
      I take pride in writing quality code that delivers value to its users and my journey to balance short-term business goals against long-term developer speed have made me a fervent believer in Agile, TDD, and constant refactoring.
      I am used to working independently in a fast-paced, changing environment and love challenging problems that help me learn and grow.
      If you know any position that fits this description, please get in touch! ;) 
      
      \null\hfill {\scriptsize Fun fact? This CV was made with LaTeX; check my ``LatexCV'' repository on github.}
    }


  \section{Work Experience}

    \workexp{Founder}
      {Nov 2023-Oct 2024}
      {www.tissai.com}
      {Remote}
      {Spain}
      {
        \item Personal project to develop a more structured and interactive search experience with the aim of gaining intuition into Artificial Intelligence techniques.
        \item Discovered several ways to not parse unstructured product titles (Vector Search, Keyword Discovery, Entity Recognition, etc) and ended interpreting them against a Bayesian Network developed using a locally-run LLM.
        \item The website uses SvelteKit, tailwindcss, and Storybook. The backend indexer uses Node, Typescript, PostgreSQL, Vitest, and a Python pool for the AI packages.
      }

    \workexp{Backend Lead}
      {Aug 2021-Oct 2023}
      {Cyferd}
      {Remote}
      {Spain}
      {
        \item Led a 5-person team and took a highly decoupled microservice architecture from proof-of-concept to production-ready platform and through two migrations (NAT Streaming to Kafka and Neo4j to PostgreSQL).
        \item Developed across all backend (storage logic, microservice orchestration, 3rd parties integrations, monitoring, etc) and implemented from scratch the platform's multi-tenant authentication.
        \item Promoted best practices in developer tooling (CI-CD pipelines, a devcontainer, local deployment tools, etc), and agile processes (incremental improvements, aceptance criteria, TDD, etc); and established a tradition of fortnightly training calls.
      }

    \workexp{Senior Frontend Developer}
      {Apr 2021-Aug 2021}
      {Cyferd}
      {Remote}
      {Spain}
      {
        \item Early employee in a low-code/no-code startup with a product capable of implementing any form-based app.
        \item Simplified the frontend's view engine and gave it the ability to react to user actions.
      }

    \workexp{Fullstack Javascript Developer}
      {Nov 2020-Apr 2021}
      {Gloval (Avansis)}
      {Remote}
      {Spain}
      {
        % \item Worked remotely as a consultant for Gloval renovating its software infrastructure with Javascript technologies.
        \item Developed microservice and microfrontend applications with Reactjs, Express, GraphQL, MongoDb, PostgreSQL and Docker.
        % \item Worked in a SCRUM environment and contributed practices like the walking skeleton to improve agility.
        \item Led the implementation of several projects and good practices to improve code quality and developer speed. %(monorepos, linting and formatting, improved decoupling, etc)
      }

    \workexp{Fullstack Javascript Developer}
      {Dec 2018-Jan 2020}
      {Linkproved}
      {Remote}
      {Spain}
      {
        \item Maintained the main site working with Reactjs, Express, and MongoDb.
        \item Developed and maintained a microservice for search and keyword recommendation using Gensim, Python, and Django.
        % \item Increased cohesion and decreased coupling and duplication of the code base while delivering on business goals.
        % \item Introduced end to end automated tests using Jest and Puppeteer.
        % \item Worked remotely and independently and offered suggestions on new features.
      }
 
    \workexp{Fullstack Javascript Freelancer}
      {Aug 2016-Nov 2018}
      {Self-employed}
      {Remote}
      {Spain}
      {
        \item Developed Single Page Apps, Backend Severs, Conversational Interfacesm, and Mobile Applications.
        % \item Worked in the frontend with React, Redux, Material-UI and Bootstrap among others.
        % \item Worked in the backend with Express, Nodejs, Mongo, Docker, Heroku, Python and Django.
        % \item Obtained system requirements from clients and established an agile relationship with them.
      }
   
    \workexp{NextGame Sport Cofounder}
      {May 2016-Sept 2016}
      {NextGame Sport} 
      {Manchester}
      {U.K.}
      {
        \item Co-founded an sport-predictions startup accepted into the Entrepreneurial Spark accelerator that sought to connect fans and brands together.
        % \item Developed its Javascript backend and its Ionic mobile app.
        % \item Took part in strategic decision-making, led feedback sessions and pitched to potential stakeholders.
      }
  
    \workexp{Software Engineer Intern}
      {Jul 2014-Jul 2015}
      {Microsoft} 
      {Dublin}
      {Ireland}
      {
        \item Created C\# desktop applications and cloud components to automate the localization process of Office content.
        % \item Maintained legacy components and promoted better coding practices to handle 5,000 daily assets.
        %  \item Worked in a 20-person agile team under little supervision and 
        %  in close contact with management and end users.
        % \item Consolidated technical skills in a production environment
        % \item Gained focus on business value
        % \item Experience in cloud computing and deployment with Azure
        % \item Participated in the internal Microsoft hackaton
        % \item Gained teamwork and interpersonal skills
      }
    
    \workexp{York Interdisciplinary Research Student}
      {Jul 2013-Sept 2013}
      {University of York}
      {York}
      {U.K.}
      {
        \item Developed a multithreaded Java GUI to teach Evolutionary Computation.
        % \item Led a 2-person team making appropriate recommendations and working independently to 
        % complete the project 
        % \item Gained customer focus and user oriented design experience
        % \item Practiced agile methods and improved teamworking skills while working as part of a team
        % \item Used Subversion (SVN) version control system to manage the code
      } 


  \section{Education}
   
    \educ{BSc (Hons) Computer Science with Business and Management}
      {Sept 2012 - Jun 2016}
      {University of Manchester}
      {Manchester}
      {U.K.}
      {1\textsuperscript{st} class honours}
      {
        % \item Created AI applications for playing Kalah, language processing, voice recognition, speech creation, hand-written digit recognition, spam filtering and an Stackelberg leader.
        % \item Performed strategic recommendations, business proposals, market research, financial analysis and marketing plans.
        % \item The joint degree has provided me a good balance between engineering and business oriented thinking
        % \item Developed presentation, teamworking, communication and leadership skills during workshops and team projects
        % \item Developed in Java, Python, C, Matlab, Prolog and HTML.
        % \item Learned Agile software development, software evolution challenges, the complexity of abstract data structures and
        % fundamental system architecture principles. 
        % system architecture principles (such as multithreading, caching, pipelining)
        % \item Adquired knowledge of modelling, design and testing and familiarity with Software Engineering approaches (Waterfall, UP, XP)
         \item Worked in several team projects and won the 2014 IBM Software Engineer price for the best team of the year.
      }

    \educ{Baccalaureate in Technology}
      {Sept 2010 - Jun 2012}
      {I.E.S. Gregorio Marañón}
      {Madrid}
      {Spain}
      {9.76/10 (first of cohort)}
      {
        \item Tackled university-level problems in the ``Campus Científicos de Verano'' program.
        % \item Coordinated the creation of a student school newspaper.
      }


  \section{Technical skills}

    \begin{description}
      \item[Programming Languages:] Typescript, Javascript, Node, Python, HTML, CSS, Bash/Zsh, etc.
      \item[Frameworks:] Express, SvelteKit, React, Tailwind, Jest, Vitest, ESLint, Prettier, Webpack, etc.
      \item[Storage \& Networking:] PostgreSQL, Websocket, REST, Kafka, MongoDB, Redix, etc
      \item[Other tooling:] Docker, VS Code, Git, Vim, Github Actions, Railway, Jira, Heroku, etc.
      \item[Human languages:] English \emph{(fluent)}, Spanish \emph{(fluent)}, French \emph{(intermediate)}, Japanese \emph{(beginner)}.
    \end{description}


  % \section{Voluntary experience}
     
  %   \workexp{Mathematics teacher}
  %     {May 2015}
  %     {Junior Achievement Ireland}
  %     {Dublin}
  %     {Ireland}
  %     {
  %       %  \item Taught mathematics and its applications to elementary school students using games.
  %     }

  %   \workexp{Committee member}
  %     {December 2013-Jul 2014}
  %     {Ultimate Programming Society}
  %     {Manchester}
  %     {U.K.}
  %     {
  %       %  \item Organized events to bring the latest technologies and development trends to the students of school.
  %     }

  %   \workexp{PASS Leader}
  %     {Sept 2013-Jul 2014}
  %     {University of Manchester}
  %     {Manchester}
  %     {U.K.}
  %     {
  %       %  \item Facilitated the learning and integration into university life of 1\textsuperscript{st} year students.
  %       %  \item Gained cultural and personality awareness, leadership and communication skills.
  %     }


  \section{Other notable positions}
    \begin{description}
      % \item[Novels of the West creator:] used Angular and Firebase to create a directory of English web novels.
      \item[Ex-Toastmaster member:] practiced public speaking and leadership skills for several years.
      \item[Venture Out 2015 finalist:] ended finalist in the business idea competition.
      \item[Sport Betting Professionals:] applied predictive analytics to make horse racing bets.
      \item[IMAV 2014 participant:] created a 7-digit number recognition program.
%       \item[WeetyNews cofounder:] developed a web page to find the most relevant world news by scraping and processing newspaper's twitter accounts. Worked with different frameworks and APIs. Source code published in github
%       \item[Raspberry Pi:] gained basic understanding of internet and server protocols by implementing a backup server, DNS redirection, and ssh, ftp, VNC servers
%       \item[Archlinux OS:] set up an Archlinux distribution from scratch and gained confidence in the command line, deeper understanding of system managers (windows, package, memory, processes...) and met alternative configurations (e.g. tiling window managers)
    \end{description}


\end{document}