\documentclass[10pt]{CurriculumVitae}
  
\name{Antonio Sánchez Gómez}
\phone{(+34) 655 643 552}
\email{sago.ant@gmail.com}
\githubaccount{antsago}
\linkedin{antsago}

\begin{document}

  \makeheading

  \section{Personal profile}
    {
      Senior Fullstack Javascript Developer and aspiring learning machine.
      I am used to working independently in a fast-paced, changing environment and take pride in writing quality code that delivers value to its users
      My journey to balance short-term business goals against long-term developer speed have made me a fervent believer in Agile, Test Driven Development, and improving Developer Experience.
      I am looking to continue growing, both as a person and as a developer, and open to new challenges and projects. So do not hesitate to get in touch! ;) 
      
      \null\hfill {\scriptsize Fun fact? This CV was made with Latex; check my ``LatexCV'' repository on github.}
    }


  \section{Work Experience}

    \workexp{Backend Lead}
      {Aug 2021-Now}
      {Cyferd}
      {Remote}
      {Spain}
      {
        \item Led a 5-person team that took a highly decoupled microservice architecture from proof-of-concept to production-ready platform
        \item Worked across all backend (storage logic, microservice orchestration, 3rd parties integrations, etc) and implemented from scratch the platform's multi-tenant authentication.
        \item Worked with the team through two migrations: NATS Streaming to Kafka and from Neo4j to PostgreSQL.
        \item Conceived, developed, and ultimately owned several projects to improve developer speed: CI and CD pipelines, styling and formatting enforcers, tools to easily deploy the platform locally, and a devcontainer with the development environment.
        \item Learned and promoted agile good practices like smaller prs with incremental improvements, the up-front discovery of acceptance criteria, test-driven-development and automated testing, etc.
        \item Established a tradition of fortnightly training calls, where each time a different member of the wider developer team will present to the rest on a topic of their choice, with the double goal of giving the host the opportunity to practice public speaking and spreading knowledge across the team.
      }

    \workexp{Senior Frontend Developer}
      {Apr 2021-Aug 2021}
      {Cyferd}
      {Remote}
      {Spain}
      {
        \item Early employee in a low-code/no-code startup with a product capable of implementing any type of form-based app
        \item Worked on the front-end's view engine, simplifying its code and adding the ability to react to user input (clicks, text inputs, etc)
      }

    \workexp{Fullstack Javascript Developer}
      {Nov 2020-Apr 2021}
      {Gloval (Avansis)}
      {Remote}
      {Spain}
      {
        \item Worked remotely as a consultant for Gloval renovating its software infrastructure with Javascript technologies.
        \item Developed microservice and microfrontend applications with Reactjs, Express, Graphql, MongoDb, Postgres and Docker.
        \item Worked in a SCRUM environment and contributed practices like the walking skeleton to improve agility.
        \item Led the implementation of several projects and good practices to improve code quality and developer speed. %(monorepos, linting and formatting, improved decoupling, etc)
      }
 
    \workexp{Fullstack Javascript Developer}
      {Aug 2016-Now}
      {Self-employed}
      {Remote}
      {Spain}
      {
        \item Developed Single Page Apps, Backend Severs and Conversational Interfaces and Mobile Applications.
        % \item Worked in the frontend with React, Redux, Material-UI and Bootstrap among others.
        % \item Worked in the backend with Express, Nodejs, Mongo, Docker, Heroku, Python and Django.
        % \item Obtained system requirements from clients and established an agile relationship with them.
      }

    \workexp{Fullstack Javascript Developer}
      {Dec 2018-Jan 2020}
      {Linkproved}
      {Remote}
      {Spain}
      {
        \item Maintained the main site working with Reactjs, Express and MongoDb.
        % \item Developed and maintained a microservice for search and keyword recommendation using Gensim, Python and Django.
        % \item Increased cohesion and decreased coupling and duplication of the code base while delivering on business goals.
        % \item Introduced end to end automated tests using Jest and Puppeteer.
        % \item Worked remotely and independently and offered suggestions on new features.
      }
   
    \workexp{NextGame Sport Cofounder}
      {May 2016-Sept 2016}
      {NextGame Sport} 
      {Manchester}
      {U.K.}
      {
        \item Co-founded an sport-predictions startup accepted into the
          Entrepreneurial Spark accelerator that sought to connect fans and brands together.
        % \item Developed its Javascript backend and its Ionic mobile app.
        % \item Took part in strategic decision-making, led feedback sessions and pitched to potential stakeholders.
      }
  
    \workexp{Software Engineer Intern}
      {Jul 2014-Jul 2015}
      {Microsoft} 
      {Dublin}
      {Ireland}
      {
        \item Created C\# desktop applications and cloud components to automate the localization
        process of Office content.
        % \item Maintained legacy components and promoted better coding practices to handle 5,000 daily assets.
        %  \item Worked in a 20-person agile team under little supervision and 
        %  in close contact with management and end users.
        % \item Consolidated technical skills in a production environment
        % \item Gained focus on business value
        % \item Experience in cloud computing and deployment with Azure
        % \item Participated in the internal Microsoft hackaton
        % \item Gained teamwork and interpersonal skills
      }
    
    \workexp{York Interdisciplinary Research Student}
      {Jul 2013-Sept 2013}
      {University of York}
      {York}
      {U.K.}
      {
        \item Developed a multithreaded Java GUI to teach Evolutionary Computation.
        % \item Led a 2-person team making appropriate recommendations and working independently to 
        % complete the project 
        % \item Gained customer focus and user oriented design experience
        % \item Practiced agile methods and improved teamworking skills while working as part of a team
        % \item Used Subversion (SVN) version control system to manage the code
      } 


  \section{Education}
   
    \educ{BSc (Hons) Computer Science with Business and Management}
      {Sept 2012 - Jun 2016}
      {University of Manchester}
      {Manchester}
      {U.K.}
      {1\textsuperscript{st} class honours}
      {
        % \item Created AI applications for playing Kalah, language processing, voice recognition, speech creation, hand-written digit recognition, spam filtering and an Stackelberg leader.
        % \item Performed strategic recommendations, business proposals, market research, financial analysis and marketing plans.
        % \item The joint degree has provided me a good balance between engineering and business oriented thinking
        % \item Developed presentation, teamworking, communication and leadership skills during workshops and team projects
        % \item Developed in Java, Python, C, Matlab, Prolog and HTML.
        % \item Learned Agile software development, software evolution challenges, the complexity of abstract data structures and
        % fundamental system architecture principles. 
        % system architecture principles (such as multithreading, caching, pipelining)
        % \item Adquired knowledge of modelling, design and testing and familiarity with Software Engineering approaches (Waterfall, UP, XP)
         \item Worked in several team projects and won the 2014 IBM Software Engineer price for the best team of the year.
      }

    \educ{Baccalaureate in Technology}
      {Sept 2010 - Jun 2012}
      {I.E.S. Gregorio Marañón}
      {Madrid}
      {Spain}
      {9.76/10 (first of cohort)}
      {
        \item Tackled university-level problems in the ``Campus Científicos de Verano'' program.
        % \item Coordinated the creation of a student school newspaper.
      }


  \section{Technical skills}

    \begin{description}
      % \item[Artificial Intelligence:] search, keyword recommenders, conversational interfaces (chatbots), etc.
      \item[Programming Languages:] Typescript, Javascript, HTML, CSS, Bash/Zsh (command line), Python, etc.
      \item[Frontend:] React, Webpack, ESLint, Redux, Material-UI, ApolloClient, Prettier, Angular, etc.
      \item[Backend:] Express, Node, REST, Graphql, Docker, Mongo, Postgres, Oracle, Swagger, etc. 
      \item[Other tooling:] VS Code, Git, Automated testing, Agile, Cloud deployment, Heroku, Azure, etc.
      \item[Human languages:] English \emph{(fluent)}, Spanish \emph{(fluent)}, French \emph{(intermediate)}, Japanese \emph{(beginner)}.
      % \item[Operating Systems:] Windows from XP to 10, OS X, Android, Archlinux
    \end{description}


  \section{Voluntary experience}
     
    \workexp{Mathematics teacher}
      {May 2015}
      {Junior Achievement Ireland}
      {Dublin}
      {Ireland}
      {
         \item Taught mathematics and its applications to elementary school students using games.
      }

    \workexp{Committee member}
      {December 2013-Jul 2014}
      {Ultimate Programming Society}
      {Manchester}
      {U.K.}
      {
         \item Organized events to bring the latest technologies and development trends to the students of school.
      }

    \workexp{PASS Leader}
      {Sept 2013-Jul 2014}
      {University of Manchester}
      {Manchester}
      {U.K.}
      {
         \item Facilitated the learning and integration into university life of 1\textsuperscript{st} year students.
        %  \item Gained cultural and personality awareness, leadership and communication skills.
      }


  \section{Other notable positions}
    \begin{description}
      % \item[Novels of the West creator:] used Angular and Firebase to create a directory of English web novels.
      \item[Toastmaster member:] regularly practicing public speaking and leadership skills.
      \item[Venture Out 2015 finalist:] ended finalist in the business idea competition.
      % \item[SBP Betting Professionals co-founder:] applied predictive analytics to make horse racing bets.
      \item[IMAV 2014 participant:] created a 7-digit number recognition program.
%       \item[WeetyNews co-founder:] developed a web page to find the most relevant world news by scraping and processing newspaper's twitter accounts. Worked with different frameworks and APIs. Source code published in github
%       \item[Raspberry Pi:] gained basic understanding of internet and server protocols by implementing a backup server, DNS redirection, and ssh, ftp, VNC servers
%       \item[Archlinux OS:] set up an Archlinux distribution from scratch and gained confidence in the command line, deeper understanding of system managers (windows, package, memory, processes...) and met alternative configurations (e.g. tiling window managers)
    \end{description}


\end{document}